Write Up: OSF T-Test

### 2018-06-15 Ttest-pvals/writeup.Rmd
other computer update

 When comparing the p-values of two paired groups using the t-test incorporates each cases' estimate and the sample size of each test. In a single example, say study 1, there would be $p_1$ the p-value from the orginal and $p_2$ the p-value from the replicate study. This is equivalent to $p_1=\Phi^{-1}\Big(\frac{|T_1|}{\sqrt{v_1}}\Big)$ and similar can be shown for $p_2$, so subtracting the two leads to $\Phi^{-1}\Big(\frac{|T_1|}{\sqrt{v_1}}\Big)-\Phi^{-1}\Big(\frac{|T_2|}{\sqrt{v_2}}\Big)$. This is dependent on the power of each statistical test using the $T$'s and $n$'s for each group. This scaled for k studies, the mean of the paired difference of p-values would be 
\begin{align}
\frac{1}{k} \sum_i ^k \Big[ \Phi^{-1}\Big(\frac{|T_i|}{\sqrt{v_i}}\Big)-\Phi^{-1}\Big(\frac{|T_i|}{\sqrt{v_i}}\Big) \Big]
\end{align}
This mean takes into account both the estimate and the sample size, thus the power to detect if the p-values are different from one another depends upon the power of both the original and the replicate studies.

>>>>

 When comparing the p-values of two paired groups using the t-test incorporates each cases' estimate and the sample size of each test. In a single example, say study 1, there would be $p_1$ the p-value from the orginal and $p_2$ the p-value from the replicate study. This is equivalent to $p_1=\Phi^{-1}\Big(\frac{|T_1|}{\sqrt{v_1}}\Big)$ and similar can be shown for $p_2$, so subtracting the two leads to $\Phi^{-1}\Big(\frac{|T_1|}{\sqrt{v_1}}\Big)-\Phi^{-1}\Big(\frac{|T_2|}{\sqrt{v_2}}\Big)$. This is dependent on the power of each statistical test using the $T$'s and $n$'s for each group. This scaled for k studies, the mean of the paired difference of p-values would be

$\frac{1}{k} \sum_j ^k \Big[ \Phi^{-1}\Big(\frac{|T_{1j}|}{\sqrt{v_{1j}}}\Big)-\Phi^{-1}\Big(\frac{|T_{2j}|}{\sqrt{v_{2j}}}\Big) \Big]$

This mean takes into account both the estimate and the sample size, thus the power to detect if the p-values are different from one another depends upon the power of both the original and the replicate studies.
